R Notebook

### 2021-03-13 eda.Rmd
Remaining EDA changes

load('streetrx.rdata')
streetrx <- streetrx %>% filter(api_temp == 'oxymorphone')

@@

Keep, log transform

The big one. First, let's take a look at which fields have missing values and how frequently they occur. First, the response variable

@@

```{r}
# Recode "missing" values to NA
levels(streetrx$source)[levels(streetrx$source) == ''] <- NA_character_
streetrx$source <- recode_factor(streetrx$source, 'w'=NA_character_,
                                 'Idk'=NA_character_)

levels(streetrx$source)[grepl('bluelight', levels(streetrx$source), fixed=TRUE)] <- 'bluelight'
levels(streetrx$source)[grepl('opiophile', levels(streetrx$source), fixed=TRUE)] <- 'opiophile'
```

@@

@@

```{r}
ggplot(small_ppm, aes(x=bulk_purchase, y=ppm)) + geom_boxplot()
```

@@

```{r}
t.test(ppm ~ bulk_purchase, data = small_ppm)
```

So bulk purchase looks to be a significant predictor *if* we exclude the extreme ppm values

>>>>

load('streetrx.rdata')
streetrx <- streetrx %>% filter(api_temp == 'oxymorphone')
streetrx <- streetrx %>% filter(!is.na(ppm))
streetrx$log_ppm <- log(streetrx$ppm)

@@

**Keep, log transform**

Our response. First, let's take a look at which fields have missing values and how frequently they occur. First, the response variable

@@

```{r}
# Recode "missing" values to NA
levels(streetrx$source)[levels(streetrx$source) == ''] <- 'Missing'
streetrx$source <- recode_factor(streetrx$source, 'w'='Missing',
                                 'Idk'='Missing')

streetrx$source <- recode_factor(streetrx$source,
                                 'Www.drugforum.com' = 'Internet',
                                 'Google.com' = 'Internet',
                                 'opiophile' = 'Internet',
                                 'silkroad' = 'Internet',
                                 'bluelight' = 'Internet',
                            'http://www.kentucky.com/2011/08/05/1835152/union-college-presidents-wife.html' = 'Internet')

for(website in c('bluelight', 'opiophile', 'silkroad')) {
    levels(streetrx$source)[grepl(website, levels(streetrx$source), fixed=TRUE)] <- website    
}
```

@@

```{r}
mgstr_grouped <- streetrx %>% group_by(mgstr) %>% summarise(avg=mean(log_ppm))
ggplot(mgstr_grouped, aes(x=mgstr, y=avg)) + geom_line()
```

```{r}
ggplot(streetrx, aes(x=log_ppm)) + geom_histogram(bins = 50)
```

@@

```{r}
ggplot(streetrx, aes(x=bulk_purchase, y=log_ppm)) + geom_boxplot()
```

@@

```{r}
t.test(log_ppm ~ bulk_purchase, data = streetrx)
```

So the two bulk purchase values look to have significantly different log ppm prices

## Primary Reason

```{r}
table(streetrx$Primary_Reason)
```

First of all, it seems like "reporter did not answer the question" and missing should belong to the same category. Let's see:

```{r}
t.test(streetrx[streetrx$Primary_Reason == '',]$log_ppm,
       streetrx[streetrx$Primary_Reason == '0 Reporter did not answer the question',]$log_ppm)
```
